Quotients of the magmatic operad:\\ lattice structures and convergent rewrite systems

### 2019-01-21 CAs_operads.tex
MAJ
Correction Acknowledgements et preuve proposition 3.2.5

\begin{Proposition}\label{prop:poset_CAs}
    The binary relation $\OrdCAs$ is a partial order relation on
    $\CAsAll$.
\end{Proposition}
\begin{proof}
    The binary relation $\OrdCAs$ is reflexive since there exists the
    identity morphism on $\CAs{\gamma}$ for every positive integer
    $\gamma$. Let us now assume that
    $\varphi:\CAs{\gamma''} \to \CAs{\gamma'}$ and
    $\psi:\CAs{\gamma'} \to \CAs{\gamma}$ are two operad morphisms. By
    Lemma~\ref{lem:morphism_CAs}, one has
    $\LComb{\gamma''} \CongrCAs{\gamma'} \RComb{\gamma''}$ and
    $\LComb{\gamma'} \CongrCAs{\gamma} \RComb{\gamma'}$. This implies
    that $\CongrCAs{\gamma}$ is coarser than $\CongrCAs{\gamma'}$ and
    that $\CongrCAs{\gamma'}$ is coarser that $\CongrCAs{\gamma''}$. Now,
    again by Lemma~\ref{lem:morphism_CAs}, $\psi \circ \varphi$ is an
    operad morphism. Hence, $\OrdCAs$ is transitive. Finally, let us
    assume that there exist morphisms
    $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$ and
    $\psi:\CAs{\gamma}\to\CAs{\gamma'}$. In particular,
    $\psi \circ \varphi$ and $\varphi \circ \psi$ are endomorphisms of
    $\CAs{\gamma'}$ and $\CAs{\gamma}$, respectively. From
    Lemma~\ref{lem:surjective_morphisms_CAs}, these two morphisms are
    identity morphisms, so that $\varphi$ and $\psi$ are injective. From
    Lemma~\ref{lem:injective_morphisms_CAs}, $\gamma$ and $\gamma'$ are
    equal, which proves that $\OrdCAs$ is anti-symmetric. Hence,
    $\OrdCAs$ is a partial order.
\end{proof}
\medbreak

@@

However, the completion algorithm we used depends on the chosen order on
the trees. In order to find out if the completion algorithm leads to a
finite convergent presentation using a different order, we run the
following backtracking algorithm. For every branching pair
$\left\{\Tfr_1, \Tfr_2\right\}$ which is not joinable, we recursively
try to find a completion of $\Rew$ by adding either the rule
$\Tfr_1 \Rew  \Tfr_2$ or $\Tfr_2 \Rew  \Tfr_1$.
If at any moment the rewrite relation $\RewContext$ induced by~$\Rew$
loops (that is $\RewContext$ is not antisymmetric), we simply reject it.
We do not find any finite presentation for $\CAs{4}$, $\CAs{5}$, and
$\CAs{6}$ until arity $12$. We conjecture that there is no finite
convergent presentation of $\CAs{\gamma}$ when $\gamma \geq 4$ and when
the left and the right members of the rewrite rules are trees
belonging to $\Mag$.
\medbreak

>>>>

\begin{Proposition}\label{prop:poset_CAs}
    The binary relation $\OrdCAs$ is a partial order relation on
    $\CAsAll$.
\end{Proposition}
\begin{proof}
    The binary relation $\OrdCAs$ is reflexive since there exists the
    identity morphism on $\CAs{\gamma}$ for every positive integer
    $\gamma$. It is transitive since the composite of operad morphisms is
    an operad morphism. Finally, let us assume that there exist  tow
    morphisms $\varphi:\CAs{\gamma'}\to\CAs{\gamma}$ and
    $\psi:\CAs{\gamma}\to\CAs{\gamma'}$. In particular,
    $\psi \circ \varphi$ and $\varphi \circ \psi$ are endomorphisms of
    $\CAs{\gamma'}$ and $\CAs{\gamma}$, respectively. From
    Lemma~\ref{lem:surjective_morphisms_CAs}, these two morphisms are
    identity morphisms, so that $\varphi$ and $\psi$ are injective. From
    Lemma~\ref{lem:injective_morphisms_CAs}, $\gamma$ and $\gamma'$ are
    equal, which proves that $\OrdCAs$ is anti-symmetric. Hence,
    $\OrdCAs$ is a partial order.
\end{proof}
\medbreak

@@

However, the completion algorithm we use depends on the chosen order on
the trees. In order to find out if the completion algorithm leads to a
finite convergent presentation using a different order, we run the
following backtracking algorithm. For every branching pair
$\left\{\Tfr_1, \Tfr_2\right\}$ which is not joinable, we recursively
try to find a completion of $\Rew$ by adding either the rule
$\Tfr_1 \Rew  \Tfr_2$ or $\Tfr_2 \Rew  \Tfr_1$.
If at any moment the rewrite relation $\RewContext$ induced by~$\Rew$
loops (that is $\RewContext$ is not antisymmetric), we simply reject it.
We do not find any finite presentation for $\CAs{4}$, $\CAs{5}$, and
$\CAs{6}$ until arity $12$. We conjecture that there is no finite
convergent presentation of $\CAs{\gamma}$ when $\gamma \geq 4$ and when
the left and the right members of the rewrite rules are trees
belonging to $\Mag$.
\medbreak

### 2019-01-21 Introduction.tex
Relecture exemples Grassmann
Correction Acknowledgements et preuve proposition 3.2.5

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Acknoledgements}
The authors wish to thank Maxime Lucas for helpful discussions and
Vladimir Dotsenko for his marks of interest and his bibliographic
suggestions.
\medbreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{General notations and conventions}
For any integers $a$ and $c$, $[a, c]$ denotes the set
$\{b \in \N : a \leq b \leq c\}$ and $[n]$, the set $[1, n]$. The
cardinality of a finite set $S$ is denoted by~$\# S$.
\medbreak

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Acknowledgements}
The authors wish to thank Maxime Lucas for helpful discussions and
Vladimir Dotsenko for his marks of interest and his bibliographic
suggestions.
\medbreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{General notations and conventions}
For any integers $a$ and $c$, $[a, c]$ denotes the set
$\{b \in \N : a \leq b \leq c\}$ and $[n]$, the set $[1, n]$. The
cardinality of a finite set $S$ is denoted by~$\# S$. In all this
work, $\K$ is a field of characteristic zero.
\medbreak
